Supplement 2

### 2020-09-03 paper/supplement-2.Rmd
add figure caption

---
title: "Supplement 2"
output: 
  bookdown::html_document2
bibliography: "supp-2.bib"
---

@@

```{r prisma}
  # | Imported                        | 3,863                             |
  # | After duplicates removed        | 1,954                             |
  # | After title and abstract screen | 1,373                             |
  # | Random sample full-text         | 199 (needed for 10% sample)       |
  # | Full-text included              | 137                               |
  # | Full-text excluded              | Full-text papers excluded (n=62)  |
  # |                                 | with reasons:                     |
  # |                                 | Qualitative study (n=)            |
  # |                                 | Not in english (n=)               |
  # |                                 | Unable to access full-text (n=)   |

>>>>

---
title: "Supplement 2"
output: 
  bookdown::html_document2
  # bookdown::pdf_document2
bibliography: "supp-2.bib"
---

@@

```{r prisma, fig.cap = "Write the figure caption here"}
  # | Imported                        | 3,863                             |
  # | After duplicates removed        | 1,954                             |
  # | After title and abstract screen | 1,373                             |
  # | Random sample full-text         | 199 (needed for 10% sample)       |
  # | Full-text included              | 137                               |
  # | Full-text excluded              | Full-text papers excluded (n=62)  |
  # |                                 | with reasons:                     |
  # |                                 | Qualitative study (n=)            |
  # |                                 | Not in english (n=)               |
  # |                                 | Unable to access full-text (n=)   |
